---
title: "Lab13"
author: "Jonathan Stiefel"
date: "11/10/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##### Expectations for Lab 13
The following are due at the end of the Week 13 lab period on Moodle:

  + Complete Lab13 in RStudio Cloud and turn in knitted file.
  + Complete Review Part 1 (started in Problem Session) and turn in a typed or scanned     in copy.
  + Complete Review Part 2 and turn in a typed or scanned in copy.

The following is due before the start of your Week 14 lab next week:

 + Complete Review Part 3 and turn in a typed or scanned in copy.

Review Parts 1, 2, and 3 are in the Word document titled "Lab13_Review_Assignment" posted on Moodle.

##### Learning Objective
+ Compute confidence interval for mean y value in linear regression
+ Review course material
+ Review R code you've used this semester

##### Problem 1
**Linear Regression**: Confidence interval for a mean y value ($\hat y$)

For this question we are going to look at the data from the 2008 season of Professional Golf (pga.csv), which you analyzed last week. We will be trying to predict a golfer's Fairway Accuracy (as a percentage) from their Average Driving Distance (in yards). 

Use (or recreate) the linear regression model you created in Lab 12 for average accuracy percentage versus average driving distance. Comment your code.

```{r}
pga <- read.csv("pga.csv") #reads in pga file

DD <- pga$Ave_Driving_Distance #creates driving distance variable
DA <- pga$Fairway_Accuracy #creates driving accuracy variable
L <- lm(DA~DD) #creates linear regression

plot(DD,DA,ylab = "Driving Accuracy",xlab = "Driving Distance (yds)") #plots 
abline(L, col="red",lwd=2) #plots linear regression

```


Compute and interpret a 95% confidence interval for the average accuracy percentage when the average driving distance is 302.5 yards.  Comment your code.
```{r}
predict(L,data.frame(DD=302.5),interval="confidence") #computes CI for DD=302.5
```


****
##### Course Review
Please refer to the Word file posted on Moodle titled "Lab13_Review_Assignment".  This file includes the review questions from Problem Session along with additional review questions about R. Follow the expectations instructions, written above and in the Word file.

